Guarded Recursive Type Theory via Sized Types

### 2019-01-10 code-oneclock-paper/latex/CloTT/Structure/ClockContexts.tex
Added label for sections for references
Work on types/context, added unicode symbols forr syntactic sugar of sigma

>>>>

Our goal is to make an interpretation of the syntax as defined in \Cref{sec:syntax}.
For this, we first need to interpret clock contexts and for those there are two possibilities.
It is either empty or we have a single clock.
In the first case, we use the tag \AIC{set} to indicate we interpret types and contexts as sets.
In the second case, we use \AIC{tot}, which says we work in some topos of trees.
